Roster Review (Generic)

### 2019-07-07 optimalLineup.Rmd
Working optional lineup (offense) function

---
title: "Optimal Lineup"
author: "Tom Kain"
date: "July 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rosters_by_position <- row_per_position(rosters)

rosters_by_position %>% 
  filter(!is.na(manager)) %>% 
  group_by(position) %>% 
  count() %>% 
  ungroup() -> rostered_count_by_pos

rosters_by_position %>% 
  group_by(position) %>% 
  arrange(zar %>% desc()) %>% 
  mutate(num = row_number()) %>% 
  full_join(rostered_count_by_pos, "position") %>% 
  filter(num <= n) %>% 
  summarize(median_zar = median(zar)) -> pos_median_zar

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  #FIXME two decimal places for pos_zar
  mutate(pos_zar = zar - median_zar) -> rosters_by_position

team <- rosters_by_position %>% 
  filter(team == "Plouffe There It Is!")

@@

result <- tibble(
  position = positions,
  player_id = NA
)

batters <- team %>%
  filter(type == "batter") %>% 
  arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
  select(player_id, name_full, position, pos_zar, zar)

@@

for (i in 0:length(batter_ids)) {
  print(i+1)
}
```

>>>>

---
title: "Optimal Lineup"
author: "Tom Kain"
date: "July 6, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(glue)
library(plotly)

source("R/helper.R")
```

```{r}
rosters <- load_players_with_projections()

rosters_by_position <- row_per_position(rosters)
```

```{r}

team <- rosters_by_position %>% 
  filter(team == "Deez Nuts")

@@

```

```{r}
batters <- team %>%
  filter(type == "batter") %>% 
  select(team, player_id, name_full, position, pos_zar, zar) %>% 
  arrange(zar %>% desc(), pos_zar %>% desc)

@@

team_result <- tibble(
  position = positions,
  player_id = NA
)

i <- 1

```
```{r}

batter_id <- batter_ids[i]

batter <- batters %>% 
  filter(player_id == batter_id)

batters <- batters %>% 
  add_row(
    team = team$team[1],
    player_id = batter$player_id[1],
    name_full = batter$name_full[1],
    position = "Util",
    pos_zar = -100,
    zar = batter$zar[1]
  ) %>% 
  arrange(zar %>% desc(), pos_zar %>% desc)

for (j in 1:length(batter$position)) {
  if (team_result$player_id[team_result$position == batter$position[j]] %>% is.na()) {
    batter_id -> team_result$player_id[team_result$position == batter$position[j]]
    print(paste0("Assigned ",batter$name_full," to ",batter$position[j]))

    break
  }
}

if (!batter_id %in% (team_result$player_id %>% as_factor() %>% levels())) {
  if (team_result$player_id[team_result$position == "Util"] %>% is.na()) {
    batter_id -> team_result$player_id[team_result$position == "Util"]
  }
  else {
    print(paste0("sending batter_id ", batter_id, " to bench"))
  }
}

i <- i+1

result <- batters %>% 
  mutate(position = as.character(position)) %>% 
  inner_join(team_result, c("player_id","position"))

result
```

```{r}
result %>% 
  mutate(pos_zar = if_else(
    position == "Util",
    zar,
    pos_zar
  ))
```

### 2019-07-07 rosterReview_generic.Rmd
Working optional lineup (offense) function

@@

```{r}
#TODO move to separate research
rosters_by_position <- row_per_position(rosters)

rosters_by_position %>% 
  filter(!is.na(manager)) %>% 
  group_by(position) %>% 
  count() %>% 
  ungroup() -> rostered_count_by_pos

rosters_by_position %>% 
  group_by(position) %>% 
  arrange(zar %>% desc()) %>% 
  mutate(num = row_number()) %>% 
  full_join(rostered_count_by_pos, "position") %>% 
  filter(num <= n) %>% 
  summarize(median_zar = median(zar)) -> pos_median_zar

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  #FIXME two decimal places for pos_zar
  mutate(pos_zar = zar - median_zar) -> rosters_by_position

```
```{r}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos

@@

# Averaging pos_zar by position, overall
# Does this actually indicate good/bad teams?
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  group_by(team, position) %>% 
  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar

@@

#TODO 3 OFs, players with multiple positions, avoid bench players
team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(avg_pos_zar),
            mean_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(mean_pos_zar %>% desc)

>>>>

```{r}
rosters_by_position <- row_per_position(rosters)

optimal_lineups_offense <- rosters_by_position %>% 
  optimal_lineup()

```

@@

```{r}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos

@@

# FIXME join optimal offense lineup with all pitching
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  group_by(team, position) %>% 
  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar

@@

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(avg_pos_zar),
            mean_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(mean_pos_zar %>% desc)
